\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
\usepackage{titlesec}
\usepackage[margin=1in]{geometry}

\titleformat{\paragraph}
{}
{}
{0em}
{}

\begin{document}

\begin{flushleft}
Josiah Mokobo Nyarega\\
jmnyarega@gmail.com\\
+254703922095\\
\today\\
\end{flushleft}

\paragraph{I'm excited to be applying for the Software Engineer, Frontend position at RED CIRCLE. I strongly believe in what RED CIRCLE is doing and I would love to be part of it. Empowering the African continent is one of the things I will be happy to be part of, I am impressed by what RED CIRCLE is doing. CIRCLEThis is something I would love to become part of. What is most fascinating is the Hotjar meetups that gives employees and opportunity to meet, have fun, share ideas etc.}

\paragraph{I have worked at Andela for almost three years now. I am a Frontend Software Engineer, mainly focused in Javascript, HTML, CSS and related libraries like React. In this role I worked on various projects including building the Information System at Andela and building and maintaining music distribution platform.}

\paragraph{As a frontend engineer at Andela Information System (AIS), we were able to deliver a number of features. I remember one feature that I was responsible for that enabled our users (Andela employees) to search through available skills and add them to their profiles. This feature was received really well. I later joined to work for one of Andela's Clients (Stem Disintermedia), where we built and maintaied a music distribution platform, this platform enables users to upload music, then the system will distribute their music to various music platforms such as spotify, deezer etc. I worked on this project fully remote for one and half years. In both teams we practiced Agile methodology and pair programming sessions, of which I found very beneficial.}

\paragraph{Again, Hotjar vision and culture has made a huge impression on me. I will be thrilled to work at and organization where every employee has an opportunity to advance and sharpen they skills through mentorship and pair programming.}

\paragraph{Thank you for your time,}

\begin{flushleft}
Sincerely,\\
Josiah Mokobo Nyarega\\
\end{flushleft}

\end{document}
